High angular resolution dust density and temperature maps from \Herschel\ imaging data

### 2012-10-18 documents/herschel/herschel_dust.tex

The posterior probability is proportional to the likelihood times the
prior; its logarithm is sum sum of the log likelihood and the log
prior.  Dust map inference---the determination of the solid-angle
parameters $\Omega_k$, the temperature parameters $T_k$, and the
emissivity parameters $\beta_k$ proceeds by optimization of the log
posterior probability.  The parameters so derived---maximum \foreign{a
  posteriori} or MAP---are taken to be the ``best-fit'' parameters in
what follows.  The MAP dust-map parameters depend on the data, the
spatial grid $\theta_k$, the data $d_n$, and the data noise variances
$\sigma_n$.

>>>>

The posterior probability is proportional to the likelihood times the
prior; its logarithm is sum sum of the log likelihood and the log
prior.  Dust map inference---the determination of the solid-angle
parameters $\Omega_k$, the temperature parameters $T_k$, and the
emissivity parameters $\beta_k$ proceeds by optimization of the log
posterior probability.  The parameters so derived---maximum \foreign{a
  posteriori} or MAP---are taken to be the ``best-fit'' parameters in
what follows.  The MAP dust-map parameters depend on the data, the
spatial grid $\theta_k$, the data $d_n$, and the data noise variances
$\sigma_n$.  Given the large number of parameters---three per pixel in
the dust map model---optimization is challenging.  However, the
problem is very sparse: Most parameters do not affect most data
pixels.  We use a brutal hand-built sparse optimizer that is part of
our image modeling project \TheTractor (CITATION); more about this
below.
